The Language of Generalization

### 2018-12-12 paper/comgen-paper.Rmd
reorganize data folder, proof edits to ms

author_note: >
  This paper is currently under review. Comments or suggestions are appreciated and should be directed to MHT.

@@

<!-- Certain linguistic expressions encode generalizations. -->
<!-- Language provides multiple, distinct ways of encoding generalizations. -->
The *language of generalization* covers a diverse swath of natural language expressions.
Generic language conveys generalizations about categories [e.g., "Dogs have four legs"; @Carlson1977; @Cohen1999; @Leslie2007; @Nickel2008] and is the most well-studied case generalizations in language.^[
  Some writers refer to the all of the *language of generalization* as "generic language" or generics.
  In both the empirical and theoretical literatures, however, analysis and experiments often focus only on generalizations about categories. 
  We use the more narrow-scoped terms (e.g., generics, habituals, and causals) to highlight the diversity of semantic types being predicated.
]
In contrast to statements about concrete individuals (e.g., "Rufus has four legs"), generic statements refer to inherently unobservable categories (e.g., the category of \textsc{dog}) and convey information that extends beyond the present context, a fact which children as young as 2 appreciate [@Cimpian2008].
Simple events (e.g., "John ran yesterday") can be generalized into habitual sentences (e.g., "John runs"), and even events of complex inferential types such as actual causal events (e.g., "The fire caused the smoke") can be described in generalization (e.g., "Fire causes smoke").

@@

Insofar as there is a single class of linguistic expressions that convey generalization, however, there should be something common to them all: a literal meaning that unifies generic, habitual, and causal language.
In this paper, we propose such a semantic core based on prevalence or probability and formalized using the tools of truth-functional semantics [@Montague1973; @Cohen1999].
A semantics based on probability will not be enough to subtle sensitivities to context that the language of generalization exhibit.
We propose that the meaning of generalizations is underspecified or *vague*, and that listeners derive a more precise interpretation in context using world knowledge.

The fact that generics are vague does not preclude them from being treated with formal models.
We draw upon the tools of Bayesian models of cognition [@Tenenbaum2011] to formalize the vagueness and context-dependence of generic language [@Frank2012; @GoodmanLassiter].
The Bayesian model separates the semantics of an utterance conveying a generalization from the world knowledge a listener would use to interpret the utterance, a key theoretical advancement beyond previous accounts.
<!-- By its instantiation in a formal model, this hypothesis has meaningful conditions under which it can be tested. -->
This formal model is the first of its kind to make quantitative predictions about human understanding of generalization in language.
<!-- With these ideas, we create an endorsement model, that describes what makes generalizations in language true or false. -->
<!-- Our model is the first to make quantitative predictions about human endorsements of generalizations in language. -->

@@

Generalizations are used to make predictions about events or properties of instances that an agent has yet to experience [@HumeTHN].
People readily predict that the next dog they encounter will have four legs, drinking another cup of coffee will cause jitters, and a new day will find the people that we know doing what they habitually do. 
In each case, we assign a specific exemplar $x$ to a category $k$, and make a prediction that it will have feature $f$.
This prediction can be described by a conditional probability: $P(x \in f \mid x \in k)$, the probability that $x$ will have $f$ given that it is in $k$ (formally, an instance of $k$ will be in the set of things that have $f$), which we will refer to as the *prevalence* and for convenience write as $p = P(f \mid k)$.
Our *prevalence* $p$ is a *prevalence in the mind*, a latent belief that a future instance of a category would have a particular property; others might call this projectibility [@Goodman1955].
The targets of our predictions can vary widely: They may be objects (a dog), events (an instance of coffee-drinking), or more ad-hoc types (a person on a particular day).
The properties also may vary (e.g., having fur, causing jitters, going to the gym).
Yet the mathematical description of the inductive belief is always given by a probability $P(f \mid k)$.

<!-- a useful representation  -->
<!-- How do we come to know things?  -->
<!-- How does one acquire inductive beliefs? -->
Probability is a useful representation for human generalization from observations [@Shepard1987].
If you observe several *wugs* (a novel category) that have two legs, you might infer that all wugs have two legs.
But not all properties have such strong projectibility:
Seeing a wug with broken wings tells you comparatively less about other wugs having broken wings [@Nisbett1983].
Abstract, potentially domain-specific, beliefs about the projectibility of different properties can be represented by a probability distribution over the prevalence $P(p)$ [@Kemp2007].
By assuming some generative process that could produce one's observations $o$ (i.e., a likelihood function $P(o \mid p)$), Bayes' Theorem provides the mathematically correct way to update one's prior beliefs from observations $o$: $P(o \mid d) \propto P(o \mid p) \cdot P(p)$  [@Tenenbaum2001].

@@

The language of generalization is easy to spot when a property, that could apply to an individual, is predicated of a category (e.g., "Dogs have four legs": *has four legs* could apply to an individual as in "This dog has four legs").
In the semantics literature on generics, bare plural sentences of this kind are sometimes described as *characterizing sentences* in contrast with *kind-denoting* sentences where the property can only meaningfully apply to the category as a whole (e.g., "Dinosaurs are extinct"; *extinct* cannot apply to an individual dinosaur).
<!-- Dinosaurs are exctinct ~ John is a smoker? -->
Generalization can also manifest when describing instances of an individual [*habitual language*; e.g., "John smokes"; @Carlson1977; @Carlson2005]; in this case, the particular instance being generalized is an instance of an individual (e.g., John at a particular moment in time), which also permits predication (e.g., "John smoked yesterday after dinner").
Verbs like *causes* or *makes* also seem to convey generalization, in this case, about an instance of an actual causal event (*causal language*; e.g., "Fire causes smoke"). 
Psychologists, linguists, and philosophers have long studied the language of generalization, as it appears very simple (e.g., syntactically) yet its meaning is difficult to formalize.^[
  We further distinguish the problem of formalizing a *meaning* for the language of generalization as opposed to the problem of *identifying* generalizations. 
  Syntax alone is neither necessary nor sufficient for a listener to know that the sentence conveys a generalization  (e.g., indefinite singulars can encode generalizations: "A dog has four legs" and bare plurals may not: "Dogs are on my front lawn").
  Our analysis thus begins once a sentence has been disambiguated as conveying a generalization. 
]

@@

If generalization from observations can be described by a probability $p$, it is natural to posit that same construct will be at the heart of a semantic theory of the language of generalization (Ingredient 1: Probability).
In semantics, belief updating generally passes through Boolean *truth values* [@Montague1973].
The simplest way to derive a Boolean from a scalar quantity like probability is via a *threshold semantics*: The utterance is true if the relevant scalar value is above a threshold.
For example, the literal meaning of the sentence "Some dogs have four legs" is that there is a non-zero chance that a given dog will have four legs: $\denote{some}(p) := p > 0$.
"Most dogs have four legs" can also be described as a threshold on prevalence (e.g., the chance that a dog will have four legs is greater than 50%): $\denote{most}(p) := p > 0.5$.^[
  These definitions concern the standard semantic truth conditions of quantifiers, not their pragmatic interpretations (e.g., that "some" often implies "not all").
]
Thus, the simplest semantics for a generalization would also be a threshold on the prevalence: $\denote{gen}(p, \theta) := p >\theta$.

The extreme flexibility of generalizations (e.g., "Mosquitos carry malaria"; "Birds lay eggs" vs. "Birds are female") suggests that no fixed threshold would suffice. 
Rather than throw out the threshold-semantics, we posit that the threshold is *underspecified* in the literal meaning and is contextually-determined in a way analogous to how gradable adjectives like *tall* have contextually-determined thresholds [e.g., what counts as tall for a four-year-old is different than what counts as tall for an adult; @Kennedy2007; @Lassiter2013].
We formalize this underspecification of meaning (Ingredient 2: Vagueness) by putting a probability distribution over $\theta$: $P(\theta)$ [@Lassiter2013; @Lassiter2015; cf., @Qing2014].

@@

Following @Lassiter2015, we formalize the vagueness in the meaning of generics $P(\theta)$ as a uniform distribution over the support of $P(p)$.

With these ingredients, the literal interpretation model (Eq. \ref{eq:L0}) computes a posterior interpretation distribution on prevalence by considering different possible thresholds $\theta$.
Figure\ \@ref(fig:uniformPriorSimulation) shows the model behavior assuming a uniform prevalence prior $P(p)$, perhaps representing a purely abstract property for which an interpreter has no substantive prior knowledge.
If the threshold were to be very high (e.g., $\theta = 0.75$), only the highest prevalence levels would be consistent with the utterance.
As the threshold decreases, more and more prevalence levels become compatible with the threshold (Figure\ \@ref(fig:uniformPriorSimulation)A).
The interpretation model weights the different thresholds by the probability that each is true, resulting in a posterior interpretation distribution on prevalence that favors higher prevalence levels (Figure\ \@ref(fig:uniformPriorSimulation)B).
This interpretation distribution captures the intuition that generalizations imply high prevalence, though with substantial uncertainty about the precise prevalence.

@@

# Worked examples

@@

Endorsement predictions depend upon the uncertain threshold model's interpretations, which are highly sensitive to background knowledge.
Background knowledge may be richly structured, reflecting intuitive theories about the underlying causes of different kinds of properties [cf., @Leslie2007].
This model posits, however, that the only impact of structured knowledge on truth judgments is in their implications for beliefs about prevalence, formalized in terms of a prevalence prior $P(p)$. 
<!-- \ndg{i’d save this for expt sections, and here just say that we posit intuitive priors for illustrations and introduce a method to actually elicit them below} -->
<!-- \mht{without this, we don't have an explanation for what the prevalence prior is, which is important for understanding the examples... i removed stuff about Betas, but check this again...} -->
The prevalence prior reflects a listener's beliefs about the prevalence of the feature in an unknown or unfamiliar category and be conceptualized in a theory-neutral way as a distribution over the prevalence among alternative categories (Figure\ \@ref(fig:simulations)).^[
  Alternatively, the prevalence prior can be conceptualized as a marginal distribution on prevalence derived from an intuitive theory formalized in a probabilistic language of thought [e.g., @Goodmanconcepts]. 
]
<!-- For example, think about five of your favorite kinds of animal: What percentage of each of them *are female*? What percentage of each of them *lay eggs*? -->
For example, the *lay eggs* prevalence prior should be bimodal, with substantial probability mass near 0-prevalence (since many animal categories do not have egg-layers) and a secondary component peaked around 0.5 (because among the animals with egg-layers, only the female members of the category have the property).
Conversely, the distribution over the prevalence of *being female* is unimodal and centered at 50%-prevalence, because almost all animals have female members in that proportion.
Figure\ \@ref(fig:simulations) (row 1) shows these and other intuitive prevalence priors for different properties (we introduce methods for empirically eliciting these priors in the experimental section).
We now turn our attention to the endorsement model's predictions.

@@

```{r workedExamples, results="asis"}
worked.examples <- data.frame(
  Example = c("1. Dogs bark",
              "2. Kangaroos have spots",
              "3. Robins lay eggs",
              "4. Robins are female",
              "5. Mosquitos carry malaria", 
              "6. Sharks don't eat people",
              "7. Mary handles the mail from Antarcita",
              "8. Supreme Court Justices have even social security numbers",
              "9. Elephants live in Africa and Asia"),
  `referent prevalence` = c("95%", "5%",  "50%", "50%", "5%", "85%", "0 times", "100%", "50%/50%"),
  `intuitive truth value` = c(
    "True", "False",  "True", "False",
    "True", "False","True", "False", "True" 
  ),
  `potential issue` = c(
    "Not all dogs bark",
    "Some kangaroos could have spots",
    "Only female robins (50%) lay eggs",
    "Same number that lay eggs (50%)",
    "Very few mosquitos actually carry malaria",
    "Most sharks don't eat people",
    "Consider there has never been any mail from Antarcita",
    "Consider 100% have even social security numbers",
    "Impossible for most to live in Africa and most to live in Asia, and no individual elephant lives in both Africa and Asia"
  )
) %>%
  rename("Intuitive referent prevalence" = referent.prevalence,
         "Intuitive truth value" = intuitive.truth.value,
         "Issue" = potential.issue)

@@

Often the first observation with generics is that they appear to behave like universal quantifiers (e.g., "All") that permit exceptions: Not all dogs bark, but still "Dogs bark" is true.
The uncertain threshold account immediately accomodates this example because there is no single, fixed threshold beyond which a generic statement becomes true.
Rather, listeners have uncertainty about the threshold which leads to graded interpretations (e.g., "Dogs bark" probably means *almost all* dogs bark; Figure\ \@ref(fig:simulations); column 1, row 2).
The endorsement model predicts "Dogs bark" is a rather good generic sentence (Figure\ \@ref(fig:simulations), bottom row) even though there are exceptions to the universal generalization (referent prevalence of barking among dogs shown with arrow in Figure\ \@ref(fig:simulations) row 2).

@@

A second observation regarding generics is that their truth conditions cannot be so lenient so as to always convey *existential* quantification (e.g., "Some").
Indeed, it's intuitively plausible that some kangaroos do have spots but a rational language user might feel awkward to assert the generic "Kangaroos have spots".
The model exhibits this same restraint, predicting a very low endorsement probability for this generic sentence (Figure\ \@ref(fig:simulations); column 2).
The reason is that, given the interpretation model's background knowledge about the property, the statement "Kangaroos have spots" will be interpreted like "Dogs bark": it would mean *almost all* kangaroos have spots. 
The endorsement model, which believes that very few kangaroos have spots, then would rather not endorse the statement because it would lead to a too-strong interpretation and mislead the listener.

@@

The prior distributions over the prevalence of both features are shown in Figure\ \@ref(fig:simulations) (columns 5 and 6).
As described above, the priors are different: Many animals have zero egg-layers (0% prevalence), while the vast majority of animal categories have female members in exactly the same proportion (50%).
Given this background knowledge, the generic interpretation model returns roughly the same interpretation distribution for each hypothetical utterance: In each case, the model believes roughly 50% have the property.
However, only in the case of "Robins lay eggs" does the endorsement model actually assert the generic; it does so because the listener interpretation would be more aligned with the referent prevalence in comparison to the interpretation of the null utterance, which is the prevalence prior.
In contrast, the hypothetical generic interpretation of "Robins are female" is not different from the prevalence prior and hence the generic conveys no new information; here, the generic would not be misleading but uninformative, and hence the model predicts an endorsement probability of 0.5.
Indeed, previous studies on generic endorsements have found "Robins are female" to not be rated as completely false but rather receive an intermediate endorsement level [i.e., *neither true nor false*; @Prasada2013].

@@

When the prevalence of the feature is very high, it is not necessary for the model to endorse the generic.
"Sharks don't eat people" is predicted to be a somewhat strange utterance, despite the fact that the vast majority of sharks do not eat people.^[
 We create this example as the converse of the classic example "Sharks eat people", predicted to be *true* despite low prevalence [@Leslie2007]. We reverse this example to show how the model deals with a high-prevalence feature for which the generic is predicted to be false or infelicitous.  
] 
<!-- Yet, intuitively, the generic would be misleading (similar in intuition to "Kangaroos have spots"). -->
Because for almost all animal categories, the prevalence of *not eating people* is almost 100% (very few things eat people), interpreting the statement "Sharks don't eat people" would lead one to believe that *no* sharks eat people (i.e., 100% don't eat people), which is too strong.
It is interesting to note that because of the high referent prevalence, the model is less certain of its decision, predicting an endorsement probability around 40% (i.e., somewhat false).
We will test this quantitative prediction in Experiment 1 on generic language.

@@

We posit that Mary the Antarctic mail handler is an extreme case of generalizations expressing *predictive* degrees of belief.
We expect this context sets up the expectation that any future mail coming from Antarctica will be handled by Mary. 
<!-- In Expt. 2c., we experimentally dissociated predictive probability from past frequency, finding that generalization endorsement tracked predictive probability, but not frequency. -->
<!-- We expect the same to be true with Mary: Any future mail coming from Antarctica will be handled by Mary.  -->
Thus the predictive probability that Mary will handle Antarctican mail, should there be some, is high.
Predictive probabilities often track past frequency or actual prevalence in the world, but people's internal models of how the world works can lead them to diverge. 
In this case our understanding of Mary's job leads to a strong predictive probability in the absence of past frequency evidence.
We explore this question experimentally in Exerpiment 2 on habituals.

@@

Imagine that all current Supreme Court Justice has a social security number which was an *even number*. 
"Supreme Court Justices have even social security numbers" is still considered false, even though the property holds for exactly 100\% of the category [@Cohen1999].
We predict the rejection of even social security numbered Justices is the result of our intuitive theories guiding our subjective predictive probabilities, which feed into the endorsement model.
That is, we predict observers strongly believe there is no causal relation between the evenness of one's social security number and selection for the Supreme Court, and thus would assign a roughly 50\% subjective probability to the *next* justice having an even social security number.
Then, "Supreme Court Justices have even social security numbers" would be rated by our model as similar to "Birds are female", because all professions have roughly the same probability of having employees with even social security numbers.
This example is thus the conceptual opposite of Mary the Antarctic mail handler, where our internal model of the world led us to a strong degree of belief in the property holding in the future; with the Supreme Court Justices, our internal models lead to a relatively weak degree of belief in the property holding in the future.

@@

Understanding how a semantic representation *composes* is another important test for a theory of generalizations in language.
@Nickel2008 suggests that "Elephants live in Africa and Asia" is troubling for prevalence-based accounts [in particular, majority-quantificational accouts where the generic means *more than half*; @Cohen1999] because the statement should be semantically equivalent to "Elephants live in Africa and elephants live in Asia".
It cannot be the case that most (more than half of) elephants live in Africa and *most* (more than half of) elephants live in Asia, unless we are to posit *international elephants* (i.e., individual elephants who live part-time in Africa and part-time in Asia), which are intuitively implausible.
<!-- However, this is the only interpretation available if the generalization is given a fixed, majority-based quantificational semantics, as posited in most statistical views of generics [e.g., if the generic means *most*; @Cohen1999]. -->

>>>>

author_note: >
  This paper is based on a Ph.D. dissertation submitted to Stanford University. The research was supported by National Science Foundation Graduate Research Fellowship DGE-114747 awarded to MHT and DARPA PPAML grant FA8750-14-2-0009 to NDG. A portion of this paper (Case Study 2) appeared in the proceedings of the 38th Annual Meeting of the Cognitive Science Society, Philadelphia, 2016. We are deeply grateful to Ellen Markman, Gregory Scontras, Thomas Icard, Michael C. Frank, Michael Franke, and Sophie Bridgers for extensive conversations about and support for this work. In addition, the work was greatly improved through countless discussions with members of the Computation and Cognition Lab and the Language and Cognition Lab at Stanford, as well as the participants of *A Generic Workshop* at the Center for the Study of Language and Information (CSLI) at Stanford in May 2017. Finally, we thank two anonymous reviewers and Joshua Hartshorne for helping us clarify our main arguments and improving the quality of the manuscript. All models, analyses, data, and links to experiments used in this article can be found at https://github.com/mhtess/genlang-paper

@@

<!-- Certain linguistic expressions encode generalizations. -->
<!-- Language provides multiple, distinct ways of encoding generalizations. -->
The *language of generalization* covers a diverse swath of natural language expressions.
Generic language conveys generalizations about categories [e.g., "Dogs have four legs"; @Carlson1977; @Cohen1999; @Leslie2007; @Nickel2008] and is the most well-studied case of generalizations in language.^[
  Some writers refer to the all of the *language of generalization* as "generic language" or generics.
  In both the empirical and theoretical literatures, however, analysis and experiments often focus only on generalizations about categories. 
  We use the more narrow-scoped terms (e.g., generics, habituals, and causals) to highlight the diversity of semantic types being predicated.
]
In contrast to statements about concrete individuals (e.g., "Rufus has four legs"), generic statements refer to inherently unobservable categories (e.g., the category of \textsc{dog}) and convey information that extends beyond the present context, a fact which children as young as 2 appreciate [@Cimpian2008].
Simple events (e.g., "John ran yesterday") can be generalized into habitual sentences (e.g., "John runs"), and even events of complex inferential types such as actual causal events (e.g., "The fire caused the smoke") can be described in generalization (e.g., "Fire causes smoke").

@@

Insofar as there is a single class of linguistic expressions that convey generalization, however, there should be something common to them all: a literal meaning that unifies generic, habitual, and causal language.
In this paper, we propose such a semantic core based on prevalence and formalized using the tools of truth-functional semantics [@Montague1973; @Cohen1999].
A semantics based on prevalence will not be enough to capture subtle sensitivities to context that the language of generalization exhibit.
We propose that the meaning of generalizations is underspecified or *vague*, and that listeners derive a more precise interpretation in context using probabilistic world knowledge.

The fact that generics are vague does not preclude them from being treated with formal models.
We draw upon the tools of Bayesian models of cognition [@Tenenbaum2011] to formalize the vagueness and context-dependence of generic language [@Frank2012; @GoodmanLassiter].
The Bayesian model separates the semantics of an utterance conveying a generalization from the world knowledge a listener would use to interpret the utterance, a key theoretical advancement beyond previous accounts.
<!-- By its instantiation in a formal model, this hypothesis has meaningful conditions under which it can be tested. -->
This formal model is the first of its kind to make quantitative predictions about human understanding of the l anguage of generalization.
<!-- With these ideas, we create an endorsement model, that describes what makes generalizations in language true or false. -->
<!-- Our model is the first to make quantitative predictions about human endorsements of generalizations in language. -->

@@

Generalizations are used to make predictions about events or properties of instances that an agent has yet to experience [@HumeTHN].
People readily predict that the next dog they encounter will have four legs, drinking another cup of coffee will cause jitters, and a new day will find the people that we know doing what they habitually do. 
In each case, we assign a specific exemplar $x$ to a category $k$, and make a prediction that it will have feature $f$.
This prediction can be described by a conditional probability: $P(x \in f \mid x \in k)$, the probability that $x$ will have $f$ given that it is in $k$ (formally, an instance of $k$ will be in the set of things that have $f$), which we will refer to as the *prevalence* and for convenience write as $p = P(f \mid k)$.
The *prevalence* $p$ is a *prevalence in the mind*, a latent belief that a future instance of a category would have a particular property; others might call this projectibility [@Goodman1955].
The targets of our predictions can vary widely: They may be objects (a dog), events (an instance of coffee-drinking), or more ad-hoc types (a person on a particular day).
The properties also may vary (e.g., having fur, causing jitters, going to the gym).
Yet the mathematical description of the inductive belief is always given by a probability $P(f \mid k)$.

<!-- a useful representation  -->
<!-- How do we come to know things?  -->
<!-- How does one acquire inductive beliefs? -->
Probability is a useful representation for human generalization from observations [@Shepard1987].
If you observe several *wugs* (a novel category) that have two legs, you might infer that all wugs have two legs.
But not all properties have such strong projectibility:
Seeing a wug with broken wings tells you comparatively less about other wugs having broken wings [@Nisbett1983].
Abstract, potentially domain-specific, beliefs about the projectibility of different properties can be represented by a probability distribution over the prevalence $P(p)$ [@Kemp2007].
By assuming some generative process that could produce one's observations $o$---a likelihood function $P(o \mid p)$---Bayes' Theorem provides the mathematically correct way to update one's prior beliefs from observations: $P(p \mid o) \propto P(o \mid p) \cdot P(p)$  [@Tenenbaum2001].

@@

The language of generalization is easy to spot when a property, that could apply to an individual, is predicated of a category (e.g., "Dogs have four legs": *has four legs* could apply to an individual as in "Rufus has four legs").
In the semantics literature on generics, bare plural sentences of this kind are sometimes described as *characterizing sentences* in contrast with *kind-denoting* sentences where the property can only meaningfully apply to the category as a whole (e.g., "Dinosaurs are extinct"; *extinct* cannot apply to an individual dinosaur).
<!-- Dinosaurs are exctinct ~ John is a smoker? -->
Generalization can also manifest when describing instances of an individual [*habitual language*; e.g., "John smokes"; @Carlson1977; @Carlson2005]; in this case, the particular instance being generalized is an instance of an individual (e.g., John at a particular moment in time), which also permits predication (e.g., "John smoked yesterday after dinner").
Verbs like *causes* or *makes* also seem to convey generalization, in this case, about an instance of an actual causal event (*causal language*; e.g., "Fire causes smoke"). 
Psychologists, linguists, and philosophers have long studied the language of generalization, as it appears very simple (e.g., syntactically) yet its meaning is difficult to formalize.^[
  We further distinguish the problem of formalizing a *meaning* for the language of generalization from the problem of *identifying* generalizations. 
  Syntax alone is neither necessary nor sufficient for a listener to know that the sentence conveys a generalization  (e.g., indefinite singulars can encode generalizations: "A dog has four legs" and bare plurals may not: "Dogs are on my front lawn").
  Our analysis thus begins once a sentence has been disambiguated as conveying a generalization. 
]

@@

Our model of interpreting the language of generalizations has three conceptual components: Probability, vagueness, and context.
If generalization from observations can be described by a probability $p$, it is natural to posit that same construct will be at the heart of a semantic theory of the language of generalization (Ingredient 1: Probability).
In semantics, belief updating generally passes through Boolean *truth values* [@Montague1973].
The simplest way to derive a Boolean from a scalar quantity like probability is via a *threshold semantics*: The utterance is true if the relevant scalar value is above a threshold.
For example, the literal meaning of the sentence "Some dogs have four legs" is that there is a non-zero chance that a given dog will have four legs: $\denote{some}(p) := p > 0$.
"Most dogs have four legs" can also be described as a threshold on prevalence (e.g., the chance that a dog will have four legs is greater than 50%): $\denote{most}(p) := p > 0.5$.^[
  These definitions concern the standard semantic truth conditions of quantifiers, not their pragmatic interpretations (e.g., that "some" often implies "not all").
]
Thus, the simplest semantics for a generalization would also be a threshold on the prevalence: $\denote{gen}(p, \theta) := p >\theta$.

The extreme flexibility of generalizations (e.g., "Mosquitos carry malaria"; "Birds lay eggs" vs. "Birds are female") suggests that no fixed threshold would suffice. 
Rather than throw out the threshold-semantics, we posit that the threshold is *underspecified* in the literal meaning and is contextually-determined in a way analogous to how gradable adjectives like *tall* have contextually-determined thresholds [e.g., what counts as tall for a person is different than what counts as tall for a building; @Kennedy2007; @Lassiter2013].
We formalize this underspecification of meaning (Ingredient 2: Vagueness) by putting a probability distribution over $\theta$: $P(\theta)$ [@Lassiter2013; @Lassiter2015; cf., @Qing2014].

@@

Following @Lassiter2015, we formalize the vagueness in the meaning of generalizations $P(\theta)$ as a uniform distribution over the support of $P(p)$.

With these ingredients, the literal interpretation model (Eq. \ref{eq:L0}) computes a posterior interpretation distribution on prevalence by considering different possible thresholds $\theta$.
Figure\ \@ref(fig:uniformPriorSimulation) shows the model behavior assuming a uniform prevalence prior $P(p)$, representing a purely abstract property for which an interpreter has no substantive prior knowledge.
If the threshold were to be very high (e.g., $\theta = 0.75$), only the highest prevalence levels would be consistent with the utterance.
As the threshold decreases, more and more prevalence levels become compatible with the threshold (Figure\ \@ref(fig:uniformPriorSimulation)A).
The interpretation model weights the different thresholds by the probability that each is true, resulting in a posterior interpretation distribution that favors higher prevalence levels (Figure\ \@ref(fig:uniformPriorSimulation)B).
This interpretation distribution captures the intuition that generalizations imply high prevalence, though with substantial uncertainty about the precise quantity.

@@

## Worked examples

@@

Endorsement predictions depend upon the uncertain threshold model's interpretations, which are highly sensitive to the interpretation model's background knowledge.
Background knowledge may be richly structured, reflecting intuitive theories about the underlying causes of different kinds of properties [cf., @Leslie2007].
Our model posits, however, that the only impact of structured knowledge on truth judgments is in their implications for beliefs about prevalence, formalized in terms of a prevalence prior $P(p)$. 
<!-- \ndg{i’d save this for expt sections, and here just say that we posit intuitive priors for illustrations and introduce a method to actually elicit them below} -->
<!-- \mht{without this, we don't have an explanation for what the prevalence prior is, which is important for understanding the examples... i removed stuff about Betas, but check this again...} -->
The prevalence prior reflects a listener's beliefs about the prevalence of the feature in an unknown or unfamiliar category and be conceptualized in a theory-neutral way as a distribution over the prevalence among alternative categories (Figure\ \@ref(fig:simulations)).^[
  Alternatively, the prevalence prior can be conceptualized as a marginal distribution on prevalence derived from an intuitive theory formalized in a probabilistic language of thought [e.g., @Goodmanconcepts]. 
]
<!-- For example, think about five of your favorite kinds of animal: What percentage of each of them *are female*? What percentage of each of them *lay eggs*? -->
For example, the *lay eggs* prevalence prior should be bimodal, with substantial probability mass near 0-prevalence (since many animal categories do not have egg-layers) and a secondary component peaked around 50% (because among the animals with egg-layers, only the female members of the category have the property).
Conversely, the distribution over the prevalence of *being female* is unimodal and centered at 50%-prevalence, because almost all animals have female members in that proportion.
Figure\ \@ref(fig:simulations) (row 1) shows these and other intuitive prevalence priors for different properties (we introduce methods for empirically eliciting these priors in the experimental section).
We now turn our attention to the endorsement model's predictions.

@@

```{r workedExamples, results="asis"}
worked.examples <- data.frame(
  Example = c("1. Dogs bark",
              "2. Kangaroos have spots",
              "3. Robins lay eggs",
              "4. Robins are female",
              "5. Mosquitos carry malaria", 
              "6. Sharks don't eat people",
              "7. Mary handles the mail from Antarcita",
              "8. Supreme Court Justices have even social security numbers",
              "9. Elephants live in Africa and Asia"),
  `referent prevalence` = c("95%", "5%",  "50%", "50%", "5%", "95%", "0 times", "100%", "50%/50%"),
  `intuitive truth value` = c(
    "True", "False",  "True", "False",
    "True", "False","True", "False", "True" 
  ),
  `potential issue` = c(
    "Not all dogs bark",
    "Some kangaroos could have spots",
    "Only female robins (50%) lay eggs",
    "Same number that lay eggs (50%)",
    "Very few mosquitos actually carry malaria",
    "Most sharks don't eat people",
    "Consider there has never been any mail from Antarcita",
    "Consider 100% have even social security numbers",
    "Impossible for most to live in Africa and most to live in Asia, and no individual elephant lives in both Africa and Asia"
  )
) %>%
  rename("Intuitive referent prevalence" = referent.prevalence,
         "Intuitive truth value" = intuitive.truth.value,
         "Issue" = potential.issue)

@@

Often the first observation with generics is that they appear to behave like universal quantifiers (e.g., "All") that permit exceptions: Not all dogs bark, but still "Dogs bark" is true.
The uncertain threshold account immediately accomodates this example because there is no single, fixed threshold beyond which a generic statement becomes true.
Rather, listeners have uncertainty about the threshold which leads to graded interpretations (e.g., "Dogs bark" means almost all dogs bark; Figure\ \@ref(fig:simulations); column 1, row 2).
The endorsement model then predicts "Dogs bark" is a rather good generic sentence (Figure\ \@ref(fig:simulations), bottom row) even though there are exceptions to the universal generalization (referent prevalence of barking among dogs roughly 95%, shown with arrow in Figure\ \@ref(fig:simulations) row 2).

@@

A second observation regarding generics is that their truth conditions cannot be so lenient so as to always convey existential quantification (e.g., "Some").
Indeed, it's intuitively plausible that some kangaroos do have spots but a rational language user might feel awkward to assert the generic "Kangaroos have spots".
The model exhibits this same restraint, predicting a very low endorsement probability for this generic sentence (Figure\ \@ref(fig:simulations); column 2).
The reason is that, given the interpretation model's background knowledge about the property, the statement "Kangaroos have spots" will be interpreted like "Dogs bark": it would mean almost all kangaroos have spots. 
The endorsement model, which believes that very few kangaroos have spots, then would rather not endorse the statement because it would lead to a too-strong interpretation and mislead the listener.

@@

The prior distributions over the prevalence of both features are shown in Figure\ \@ref(fig:simulations) (columns 5 and 6).
As described above, the priors are different: Many animals have zero egg-layers (0% prevalence), while the vast majority of animal categories have female members in exactly the same proportion (50%).
Given this background knowledge, the generic interpretation model returns roughly the same interpretation distribution for each hypothetical utterance: In each case, the model believes roughly 50% have the property.
However, only in the case of "Robins lay eggs" does the endorsement model actually assert the generic; it does so because the listener interpretation would be more aligned with the referent prevalence in comparison to the interpretation of the null utterance, which is the prevalence prior.
In contrast, the hypothetical generic interpretation of "Robins are female" is not different from the prevalence prior and hence the generic conveys no new information; here, the generic would not be misleading but uninformative, and hence the model predicts an endorsement probability of 0.5.
Indeed, previous studies on generic endorsements have found "Robins are female" to not be rated as completely false but rather receive an intermediate endorsement level [i.e., neither true nor false; @Prasada2013].

@@

When the prevalence of the feature is very high, it is not necessary for the model to endorse the generic.
"Sharks don't eat people" is predicted to be a somewhat strange utterance, despite the fact that the vast majority of sharks do not eat people.^[
 We create this example as the converse of the classic example "Sharks eat people", predicted to be *true* despite low prevalence [@Leslie2007]. We reverse this example to show how the model deals with a high-prevalence feature for which the generic is predicted to be false or infelicitous.  
] 
<!-- Yet, intuitively, the generic would be misleading (similar in intuition to "Kangaroos have spots"). -->
Because for almost all animal categories, the prevalence of *not eating people* is almost 100% (very few things eat people), interpreting the statement "Sharks don't eat people" would lead one to believe that no sharks eat people (i.e., 100% don't eat people), which is too strong.
It is interesting that because of the high referent prevalence, the model is less certain of its decision, predicting an endorsement probability around 0.4 (i.e., somewhat false).
We will test this quantitative prediction in Experiment 1 on generic language.

@@

We posit that Mary the Antarctic mail handler is an extreme case of generalizations expressing *predictive* degrees of belief.
We expect this context sets up the expectation that any future mail coming from Antarctica will be handled by Mary. 
<!-- In Expt. 2c., we experimentally dissociated predictive probability from past frequency, finding that generalization endorsement tracked predictive probability, but not frequency. -->
<!-- We expect the same to be true with Mary: Any future mail coming from Antarctica will be handled by Mary.  -->
Thus the predictive probability that Mary will handle Antarctic mail, should there be some, is high.
Predictive probabilities often track past frequency or actual prevalence in the world, but people's internal models of how the world works can lead the two to diverge. 
In this case our understanding of Mary's job leads to a strong predictive probability in the absence of past frequency evidence.
We explore this question experimentally in Exerpiment 2 on habituals.

@@

Imagine that all current Supreme Court Justice has a social security number which was an even number.
"Supreme Court Justices have even social security numbers" is still considered false, even though the property holds for exactly 100\% of the category [@Cohen1999].
We predict the rejection of even social security numbered Justices is the result of people's intuitive theories guiding their subjective predictive probabilities, which feed into the endorsement model.
That is, we predict observers strongly believe there is no causal relation between the evenness of one's social security number and selection for the Supreme Court, and thus would assign a roughly 50\% subjective probability to the next justice having an even social security number.
Then, "Supreme Court Justices have even social security numbers" would be rated by our model as similar to "Birds are female", because all professions have roughly the same probability of having employees with even social security numbers.
This example is thus the conceptual opposite of Mary the Antarctic mail handler, where our internal model of the world led us to a strong degree of belief in the property holding in the future; with the Supreme Court Justices, our internal models lead to a relatively weak degree of belief in the property holding in the future.

@@

Understanding how a semantic representation composes is another important test for a theory of the language of generalization.
@Nickel2008 suggests that "Elephants live in Africa and Asia" is troubling for prevalence-based accounts [in particular, majority-quantificational accouts where the generic means *more than half*; @Cohen1999] because the statement should be semantically equivalent to "Elephants live in Africa and elephants live in Asia".
It cannot be the case that most (more than half of) elephants live in Africa and most (more than half of) elephants live in Asia, unless we are to posit international elephants (i.e., individual elephants who live part-time in Africa and part-time in Asia), which are intuitively implausible.
<!-- However, this is the only interpretation available if the generalization is given a fixed, majority-based quantificational semantics, as posited in most statistical views of generics [e.g., if the generic means *most*; @Cohen1999]. -->
